### 2022-03-26 chapters/conclusions/conclusions.tex
modif post-defense - part I

@@

>>>>

\modif{\section{Developments of the model}}

\modif{Answering the aforementioned research questions required the development of new modeling tools. As this thesis heavily relies on Lagrangian transport modeling, several features were added to the particle tracker of SLIM. Although the transport of the particles in itself was already implemented in the model, we developed features to characterize the state of the particles and compute connectivity indicators. The particle state can be used to represent biological traits such as the competency of coral larvae or abiotic characteristics such as the decaying mass of diseased material or the diameter of sediment particles. We developed tools to derive connectivity indicators such as the shortest paths between a pair sub-reef polygons in the obtained  connectivity network. Additionally, we developed an epidemiological model using the computed connectivity matrices to simulated the spread of the stony coral tissue loss disease throughout Florida. Finally, the particle tracker was made more flexible by adding the capability to transport particles using outputs from larger-scale ocean models such as HYCOM.}

\modif{Additionally, the coupling of SLIM with SWAN required some modifications of SLIM. First, we implemented a new parameterization of the wind drag coefficient to account for the formation of spume at the ocean-atmosphere interface in heavy wind conditions. Furthermore, a term was added to the model's equations to account for the gradient of atmospheric pressure generated at the center of the hurricane. Using SWAN also required the implementation of tools to process wave spectrum and parameters in SLIM. The implementation of the coupling between the two models was based on the ADCIRC+SWAN model. It required the development of tools to convert SLIM outputs and forcing into SWAN format, and to allow SLIM to read SWAN outputs. Compared to the ADCIRC+SWAN, an additional challenge that we had to overcome was the fact that SLIM is based on discontinous Galerkin finite element models while SWAN requires continuous fields on the mesh. This was especially critical when defining the communication between the nodes of the partitions of SWAN based on the partitioning of the mesh used in SLIM.}

\modif{However, the implementation of the coupling could be improved, as the two models are currently alternatively run and stopped with different initial and boundary conditions. The coupling therefore induces unwanted initialization computational costs each time one of the two model is run. Suppressing these initialization costs would strongly reduce the overhead of the coupling. Furthermore, a strong limitation of the coupled model is the temporal complexity of SWAN, which runs four times slower than SLIM. A way to tackle this issue would be to run SWAN on a smaller, coarser mesh than SLIM to reduce its computation time at the expense of a potentially reduced resolution in the wave outputs. Alternatively, as robust estimates of the Stokes drift can be derived from the surface wind speed \citep{ardhuin2009observation}, a one-way coupled wave-current model could be developed using the vortex force formalism. In such a model, wave impact on currents would be modeled in SLIM through interactions between a wind-parameterized Stokes drift and the vorticity of the modeled currents, as in \cite{curcic2015explicit}.} \newline

@@

\modif{\subsection*{Better understanding the impact of hurricanes on corals}}
\modif{In this thesis, the impact of hurricanes on coral reef ecosystems was mostly evaluated by modeling wave-induced advective transport processes. However, when studying the propagation of drifting particles, assessing the impact of hurricanes on the dispersion of the particle cloud is also of interest. This could be performed by computing the distance between the positions of the particles of the cloud and its center of mass or by evaluating the evolution of the concentration of particles in the cloud. Furthermore, wave-induced transport is not the only way tropical cyclones affect coral reef biota. First, they cause mechanic damages to the reefs as they pass over them. However, this destruction can have positive consequences by facilitating asexual recruitment and cleaning algal overgrowth on the reefs \citep{banks2008reef}. Furthermore, hurricanes increase water turbidity and induce coral burial by resuspending sediments. These impacts could be assessed by combining the developed coupled wave-current model with our sediment transport model. Moreover, hurricane interact with the Florida Current by disrupting its vertical structure and reducing its transport. These structural perturbations might have consequences on eddy activity and baroclinic instabilities near the Florida Keys. Our study could therefore be extended by evaluating the impact of Hurricane Irma on the ocean state and the broader circulation patterns in Florida. Finally, by modifying the ocean circulation on their passage, hurricanes might influence the propagation of SCTLD through Florida's Coral Reef. Hurricane Irma could therefore have acted as a "super spreader" of disease agents or as a barrier to the propagation of the outbreak. This effect could be investigated by combining SLIM+SWAN with the developed epidemiological model.} \newline

### 2022-03-26 chapters/intro/intro.tex
modif post-defense - part I

\begin{figure}
    \centering
    \includegraphics[width=.9\textwidth]{chapters/intro/figures/cover.jpeg}
    \caption{Evolution of the absolute coral cover in the Caribbean. Source: \cite{gardner2003long}}
    \label{intro:cover}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{chapters/intro/figures/fig_sctld.png}
    \caption{Propagation of the SCTLD troughout the FRT between 2014 and 2021}
    \label{intro:propagation}
\end{figure}

@@

These objectives can be summarized into four main questions:
\begin{enumerate}
    \item How did the SCTLD spread through the FRT ?
    \item What caused the apparent stalling of the propagation of SCTLD ? 
    \item What was the impact of the PMDDP on the onset of the oubreak of SCTLD~?
    \item  What is the effect of hurricane-induced wave-current interactions on transport processes and should they be taken into account when modeling the dispersal of coral larvae ?
\end{enumerate}     
Answering these four questions required the use of an ocean model able to capture both the large-scale ocean features influencing circulation along the FRT as well as small-scale flow features down to the reef scale. A description of the main hydrodynamic features of the FRT as well as an overview of the modeling tools used in this thesis are given in the next section.

\section{Modeling hydrodynamics and transport processes in the FRT}
The FRT is located along the northern side of the Straits of Florida, that connects the Gulf of Mexico (GoM) and the North Atlantic Ocean. The large-scale circulation in this region is dominated by the interplay of the Florida Current (FC) and the Loop Current (LC). The LC is an area of warm waters from the Caribbean Sea that enters the GoM through the Yucatan Channel and then loops anti-cyclonically through the northeastern Gulf of Mexico and finally exits through the southern Straits of Florida, where it forms the Florida Current (FC). The FC then flows northward between Florida and the Great Bahama Bank to form the Gulf Stream (Fig. \ref{intro:gom}). The northward penetration of the LC through the GoM varies throughout the year, and sporadically an anticyclonic ring separates from the current \citep{leipper1970sequence, maul1977annual, vukovich1988loop}. The detachment of these anticyclonic eddies from the main LC affects in turn the position of the FC, causing its meandering along the FRT. These variations of the FC position have been shown to have no seasonal pattern, and a strong interannual variability. The generated meandering is associated with the presence of cyclonic eddies between the core of the current and the FRT \citep{kourafalou2012florida}. These eddies significantly impact the ecology of the southwest Florida Shelf by causing larval retention on the shelf and delivering larval pulses to the Upper Keys \citep{lee1994evolution,limouzy1997translocation,sponaugle2005florida, kourafalou2012florida}. Furthermore, when the LC meets the shallow waters of the southwest corner of the WFS near the DRTO, it causes the inflow of nutrients that modify water properties on the shelf \citep{weisberg2003local, liu2016offshore}. These contacts have been hypothesized to impact in turn the penetration of the LC in the GoM \citep{weisberg2017loop}. However, on the northernmost section of the FRT, eddies generated by the meandering of the FC cause cold-water upwelling limiting the northern range of tropical species \citep{walker2013determining}. The circulation on the upper part of the shelf along the FRT is largely influenced by winds, as well as diurnal and semi-diurnal tidal processes \citep{lee2001transport, lee2002volume,d2007patterns}

@@

In this thesis, we used the 2D barotropic version of the unstructured-mesh Second-generation Louvain-la-Neuve Ice-ocean Model (\href{https://www.slim-ocean.be/}{SLIM}). This model relies on Discontinuous Galerkin finite element methods \citep{aizinger2002discontinuous} and has already been successfully used to model the hydrodynamics of the whole Great Barrier Reef \citep{lambrechts2008multi}. Moreover, by coupling SLIM with GOM-HYCOM, the model was able to indirectly represent the baroclinic dynamics of the FC. Using this coupling, \cite{frys2020fine} successfully modeled coral larval connectivity in the FRT, \ie~the exchanges of larvae between reefs. In this study, coral larvae were modeled using a Lagrangian particle tracking model \citep{van2018lagrangian} forced by SLIM currents. To answer our different research questions, we adapted this larval transport model to evaluate the dispersal of the causative agent of the SCTLD and sediments particles.

@@

\section*{Outline}
This thesis is mainly a collection of publications describing our answers to our four main research questions. Chapter \ref{chap:sctld} describes the development of a coupled epidemio-hydrodynamic model to reproduce the observed spread of SCTLD in the FRT. Chapter \ref{chap:drto} explains how this model was used to study the apparent stalling of the spread of the SCTLD between the Marquesas and the DRTO. Chapter \ref{chap:onset} investigates the impact of the PMDDP on the onset of the SCTLD oubreak in 2014. Chapter \ref{chap:irma} describes the development of a coupled wave-current model to study the impacts of Hurricane Irma (2017) on wave-induced transport processes in the Florida Keys. Finally, chapter \ref{chap:conclusion} presents the conclusions of this thesis and perspectives for further works.

@@

\end{list}
\newpage 
\section{List of acronyms and abbreviations}

\begingroup
    \setlength{\tabcolsep}{20pt}
    \renewcommand{\arraystretch}{1.3}
    \begin{tabular}{ll}
        \textbf{DRTO}   & Dry Tortugas \\
        \textbf{ECMWF}  & European Centre for Medium-Range Weather Forecast \\
        \textbf{D55}    & Dredge 55 clamshell \\
        \textbf{FC}     & Florida Current \\
        \textbf{FCR}    & Florida's Coral Reef \\
        \textbf{FRT}    & Florida Reef Tract  \\
        \textbf{GoM}    & Gulf of Mexico \\
        \textbf{HURDAT} & HURricane DATabases \\
        \textbf{HYCOM}  & HYbrid Coordinate Ocean Model \\
        \textbf{LC}     & Loop Current \\
        \textbf{NOAA}   & National Oceanographic and Atmospheric Administration \\
        \textbf{ODMDS}	& Ocean Dredge Material Disposal Site \\
        \textbf{PoM}    & Port of Miami \\
        \textbf{PMDDP}  & PortMiami Deep Dredge Project \\
        \textbf{RS}     & Radiation stress \\
        \textbf{SB}     & Spider Barge \\
        \textbf{SCTLD}  & Stony coral tissue loss disease \\
        \textbf{SLIM}   & Second-generation Louvain-la-Neuve Ice-ocean Model\\
        \textbf{SWAN}   & Simulating WAves Nearshore \\
        \textbf{TI}     & Terrapin Island hopper \\
        \textbf{TX}     & Texas cutterhead \\
        \textbf{WWTP}	& Wastewater Treatment Plant \\
        \textbf{WFS}    & West Florida Shelf
    \end{tabular}
\endgroup

>>>>

\begin{figure}
    \centering
    \includegraphics[width=.9\textwidth]{chapters/intro/figures/cover.jpeg}
    \caption{Decline of the absolute coral cover in the Caribbean from $\sim$50\% to $\sim$10\% between 1977 and 2001. Source: \cite{gardner2003long}}
    \label{intro:cover}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{chapters/intro/figures/fig_sctld.png}
    \caption{Observed propagation of the \modif{stony coral tissue loss disease} throughout the \modif{Florida Reef Tract} between 2014 and 2021}
    \label{intro:propagation}
\end{figure}

@@

These objectives can be summarized into four main questions:
\begin{enumerate}
    \item How did the \modif{stony coral tissue loss disease} spread through Florida's Coral Reef ?
    \item What caused the apparent stalling of the propagation of the \modif{disease} ? 
    \item What was the impact of the \modif{PortMiami Deep Dredge Project} on the onset of the disease oubreak ?
    \item  What is the effect of hurricane-induced wave-current interactions on transport processes and should they be taken into account when modeling the dispersal of coral larvae ?
\end{enumerate}     
Answering these four questions required the use of an ocean model able to capture both the large-scale ocean features influencing circulation along the FRT as well as small-scale flow features down to the reef scale. A description of the main hydrodynamic features of the FRT as well as an overview of the modeling tools used in this thesis are given in the next section.

\section{Modeling hydrodynamics and transport processes in Florida's Coral Reef}
The FRT is located along the northern side of the Straits of Florida, that connects the Gulf of Mexico (GoM) and the North Atlantic Ocean. The large-scale circulation in this region is dominated by the interplay of the Florida Current (FC) and the Loop Current (LC). The LC is an area of warm waters from the Caribbean Sea that enters the GoM through the Yucatan Channel and then loops anti-cyclonically through the northeastern Gulf of Mexico and finally exits through the southern Straits of Florida, where it forms the Florida Current (FC). The FC then flows northward between Florida and the Great Bahama Bank to form the Gulf Stream (Fig. \ref{intro:gom}). The northward penetration of the LC through the GoM varies throughout the year, and sporadically an anticyclonic ring separates from the current \citep{leipper1970sequence, maul1977annual, vukovich1988loop}. The detachment of these anticyclonic eddies from the main LC affects in turn the position of the FC, causing its meandering along the FRT. These variations of the FC position have been shown to have no seasonal pattern, and a strong interannual variability. The generated meandering is associated with the presence of cyclonic eddies between the core of the current and the FRT \citep{kourafalou2012florida}. These eddies significantly impact the ecology of the southwest Florida Shelf by causing larval retention on the shelf and delivering larval pulses to the Upper Keys \citep{lee1994evolution,limouzy1997translocation,sponaugle2005florida, kourafalou2012florida}. Furthermore, when the LC meets the shallow waters of the southwest corner of the WFS near the DRTO, it causes the inflow of nutrients that modify water properties on the shelf \citep{weisberg2003local, liu2016offshore}. These contacts have been hypothesized to impact in turn the penetration of the LC in the GoM \citep{weisberg2017loop}. However, on the northernmost section of the FRT, eddies generated by the meandering of the FC cause cold-water upwelling limiting the northern range of tropical species \citep{walker2013determining}. The circulation on the upper part of the shelf along the FRT is largely influenced by winds, as well as diurnal and semi-diurnal tidal processes \citep{lee2001transport, lee2002volume,d2007patterns}

@@

In this thesis, we used the 2D barotropic version of the unstructured-mesh Second-generation Louvain-la-Neuve Ice-ocean Model (\href{https://www.slim-ocean.be/}{SLIM}). This model relies on Discontinuous Galerkin finite element methods \citep{aizinger2002discontinuous} and has already been successfully used to model the hydrodynamics of the whole Great Barrier Reef \citep{lambrechts2008multi}. \modif{The 2D version of SLIM solves the shallow water equations, which assume a constant water density and compute depth-averaged current velocities. This model is therefore well suited for shallow areas where the water-column is well mixed. Furthermore, assuming homogeneous vertical profiles reduces the computational cost and allows a finer spatial resolution of the model. In deeper areas however, 3D baroclinic models are required to capture the variations of density in the water column due to pressure, temperature and salinity. These differences in density cause baroclinic instabilities that generate mesoscale eddies. However, 3D baroclinic models are computationally more expensive, which prohibits the use of a reef-scale resolution on the whole Florida Reef Tract. As most reefs of the Florida are located in areas shallower than 30 meters [\textbf{INSERT FIGURE}], we coupled the 2D version of SLIM with GOM-HYCOM to indirectly capture the impact of baroclinic instabilities on the connectivity of the Florida Keys. Using this approach, \cite{frys2020fine} successfully modeled coral larval connectivity in the FRT, \ie~the exchanges of larvae between reefs. The results of the model used in this thesis were validated against observations and showed good agreement with tide gauge and ADCP measurements, as illustrated in appendix \ref{onset:appendice} and chapter \ref{chap:irma}}.

\modif{new paragraph: Eulerian vs Lagrangian and why Lagrangian} In this study, coral larvae were modeled using a Lagrangian particle tracking model forced by SLIM currents. To answer our different research questions, we adapted this larval transport model to evaluate the dispersal of the causative agent of the SCTLD and sediments particles. \modif{[add stuff about the bathymetry and the model validation]}

@@

\modif{\section{Modeling framework and assumptions}}

\modif{Wave-Current coupling. Radiation stress vs vector force}

\modif{Presentation of the epidemiological model ?}

\modif{Hypotheses of the model/study}\newline

\section*{Outline}
This thesis is mainly a collection of publications describing our answers to our four main research questions. Chapter \ref{chap:sctld} describes the development of a coupled epidemio-hydrodynamic model to reproduce the observed spread of SCTLD in the FRT. Chapter \ref{chap:drto} explains how this model was used to study the apparent stalling of the spread of the SCTLD between the Marquesas and the DRTO. Chapter \ref{chap:onset} investigates the impact of the PMDDP on the onset of the SCTLD oubreak in 2014. Chapter \ref{chap:irma} describes the development of a coupled wave-current model to study the impacts of Hurricane Irma (2017) on wave-induced transport processes in the Florida Keys. \modif{By lack of time, the propagation of coral larvae during Irma was not studied in this chapter}. Finally, chapter \ref{chap:conclusion} presents the conclusions of this thesis and perspectives for further works.

@@

\end{list}

### 2022-03-26 chapters/irma/article.tex
modif post-defense - part I

We followed the approach of \cite{dietrich2012performance} by characterizing the wave-induced forces on currents using the radiation-stress (RS) gradient formalism, which has been successfully applied in both 2D and 3D coupled wave-current models under storm conditions \citep{hope2013hindcast, sebastian2014characterizing, brown2013depth}. An alternative formalism is the vortex-force (VF) representation \citep{mcwilliams2004asymptotic}, that provides a clearer decomposition of the wave effect \citep{lane2007wave}. Although both approaches were adopted by coastal modeling communities, there is an ongoing scientific debate over the correctness and applicability of the two concepts \citep{ardhuin2008comments, mellor2013waves, mellor2015combined, ardhuin2017comments}. \cite{xia2020implementation} recently implemented the two formalisms in a 3D unstructured-grid model and compared them in three typical coastal systems, showing that the 3D RS algorithm could generate unrealistic offshore currents near shorelines. Despite these shortcomings, the 3D RS method reproduced most wave-induced currents and the 2D RS formalism remains a well-validated modeling approach. Furthermore, \cite{mellor2013waves} showed that the RS approach was valid when $[\frac{\partial H}{\partial\mathbf{x}}/\sinh(kh)]^2$ is smaller or of the same order as $(ka)^2$, where $a$ is the wave amplitude. We evaluated these quantities and verified that the validity criterion was met in our model domain. Additionally, since the VF and RS approached are formally equivalent \citep{lane2007wave}, we selected the 2D RS formalism, as it has the advantage of summarizing the impact of waves on the currents in a single additional stress term in the hydrodynamic model equations.

@@

To quantify the impact of wave-current interactions on transport processes, we compared the trajectories of passive particles advected by the uncoupled SLIM and coupled SLIM+SWAN currents during the passage of Irma in the Lower Keys. Furthermore, the depth-averaged Stokes drift was computed using the wave spectra of the coupled model SLIM+SWAN run as well as those of an uncoupled SWAN run. Particles were released on the inner and outer shelves at the points highlighted by red and blue dots in Fig. \ref{fig:init} on Sept. 7 at 0000 UTC and then tracked until Sept. 15. These initial particle positions were found using backtracking methods \citep{spivakovskaya2005simulation} to ensure that the release particles would intersect the path of Irma during its passage through the Florida Keys. We first defined two 25 km$^\text{2}$ circular regions on the trajectory of the hurricane (see red and blue circles in Fig. \ref{fig:init}). Particles within these two regions were then tracked backward in time using uncoupled SLIM currents from the exact time of the passage of the hurricane until Sept. 7 at 0000 UTC. Their positions at the end of the backward simulation (see red and blue particle clouds in Fig. \ref{fig:init}) corresponds to the initial condition of the forward transport simulations described below. We then compared the trajectories of particles originating from these regions and advected forward in time by different sets of currents: (i) uncoupled SLIM currents alone; (ii) coupled SLIM+SWAN currents; (iii) SLIM currents with the addition of the depth-averaged Stokes drift computed with the coupled wave-current model (Stokes-C); (iv) SLIM+SWAN currents with Stokes-C; and (v) SLIM currents with the depth-averaged Stokes drift computed with the uncoupled wave model (Stokes-U). The different combinations of Eulerian currents and Stokes drifts used to model the transport of passive drifters in the Lower Keys during the passage of Irma are summarized in Table \ref{tab:summary}. Particle trajectories are compared by computing the distances between the centers of mass of the particle clouds through time.

@@

\begin{figure}
    \centering
    \includegraphics[width=.95\textwidth]{chapters/irma/figures/validation_met_2.png}
    \caption{Comparison of reconstructed atmospheric pressure (top) and wind speed (bottom)} with field measurements and coarser ECMWF ERA-5 profiles at Vaca Key station. The generated hybrid atmospheric forcings better reproduce the observed storm depression while H*wind winds better reproduce the measured peak in wind speed.
    \label{fig:forcings}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=.99\textwidth]{chapters/irma/figures/trajectory_comparisons.png}
    \caption{Difference between the centers of mass of the particle clouds released from the regions highlighted in Fig. \ref{fig:init} and advected by the different combinations of Eulerian currents and Stokes drifts described in Table \ref{tab:summary}}.
    \label{fig:traj}
\end{figure}

>>>>

We followed the approach of \cite{dietrich2012performance} by characterizing the wave-induced forces on currents using the radiation-stress (RS) gradient formalism, which has been successfully applied in both 2D and 3D coupled wave-current models under storm conditions \citep{hope2013hindcast, sebastian2014characterizing, brown2013depth}. \modif{In this formalism, wave-averaged effects are characterized by the divergence of a stress tensor representing the flux of momentum to currents due to surface gravity waves \citep{longuet1964radiation,lane2007wave,kumar2012implementation}}. An alternative formalism is the vortex-force (VF) representation \citep{mcwilliams2004asymptotic}, that provides a clearer decomposition of the wave effect \citep{lane2007wave}. \modif{In this formalism, wave impact on current is represented by the combination of the gradient of a Bernoulli head representing adjustments to the pressure in incompressible fluids, and the interaction of the Stokes drift with the vorticity of the flow, \textit{i.e.} the vortex force \citep{lane2007wave}}. Although both approaches were adopted by coastal modeling communities, there is an ongoing scientific debate over the correctness and applicability of the two concepts \citep{ardhuin2008comments, mellor2013waves, mellor2015combined, ardhuin2017comments}. \cite{xia2020implementation} recently implemented the two formalisms in a 3D unstructured-grid model and compared them in three typical coastal systems, showing that the 3D RS algorithm could generate unrealistic offshore currents near shorelines. Despite these shortcomings, the 3D RS method reproduced most wave-induced currents and the 2D RS formalism remains a well-validated modeling approach. Furthermore, \cite{mellor2013waves} showed that the RS approach was valid when $[\frac{\partial H}{\partial\mathbf{x}}/\sinh(kh)]^2$ is smaller or of the same order as $(ka)^2$, where $a$ is the wave amplitude. We evaluated these quantities and verified that the validity criterion was met in our model domain. Additionally, since the VF and RS approached are formally equivalent \citep{lane2007wave}, we selected the 2D RS formalism, as it has the advantage of summarizing the impact of waves on the currents in a single additional stress term in the hydrodynamic model equations.

@@

To quantify the impact of wave-current interactions on transport processes, we compared the trajectories of passive particles advected by the uncoupled SLIM and coupled SLIM+SWAN currents during the passage of Irma in the Lower Keys. Furthermore, the depth-averaged Stokes drift was computed using the wave spectra of the coupled model SLIM+SWAN run as well as those of an uncoupled SWAN run. Particles were released on the inner and outer shelves at the points highlighted by red and blue dots in Fig. \ref{fig:init} on Sept. 7 at 0000 UTC and then tracked until Sept. 15. These initial particle positions were found using backtracking methods \citep{spivakovskaya2005simulation} \modif{to obtain a probabilistic picture of the release positions from which particles would intersect the path of Irma during its passage through the Florida Keys}. We first defined two 25 km$^\text{2}$ circular regions on the trajectory of the hurricane (see red and blue circles in Fig. \ref{fig:init}). Particles within these two regions were then tracked backward in time using uncoupled SLIM currents from the exact time of the passage of the hurricane until Sept. 7 at 0000 UTC. Their positions at the end of the backward simulation (see red and blue particle clouds in Fig. \ref{fig:init}) corresponds to the initial condition of the forward transport simulations described below. We then compared the trajectories of particles originating from these regions and advected forward in time by different sets of currents: (i) uncoupled SLIM currents alone; (ii) coupled SLIM+SWAN currents; (iii) SLIM currents with the addition of the depth-averaged Stokes drift computed with the coupled wave-current model (Stokes-C); (iv) SLIM+SWAN currents with Stokes-C; and (v) SLIM currents with the depth-averaged Stokes drift computed with the uncoupled wave model (Stokes-U). The different combinations of Eulerian currents and Stokes drifts used to model the transport of passive drifters in the Lower Keys during the passage of Irma are summarized in Table \ref{tab:summary}. Particle trajectories are compared by computing the distances between the centers of mass of the particle clouds through time.

@@

\begin{figure}
    \centering
    \includegraphics[width=.95\textwidth]{chapters/irma/figures/validation_met_2.png}
    \caption{Comparison of reconstructed atmospheric pressure (top) and wind speed (bottom) with field measurements and coarser ECMWF ERA-5 profiles at Vaca Key station. The generated hybrid atmospheric forcings better reproduce the observed storm depression while H*wind winds better reproduce the measured peak in wind speed.}
    \label{fig:forcings}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=.99\textwidth]{chapters/irma/figures/trajectory_comparisons.png}
    \caption{Difference between the centers of mass of the particle clouds released from the regions highlighted in Fig. \ref{fig:init} and advected by the different combinations of Eulerian currents and Stokes drifts described in Table \ref{tab:summary} \modif{In the top panels, the trajectories of particles advected by Eulerian currents from an uncoupled SLIM run are compared with trajectories obtained with Eulerian currents and Stokes drift from a coupled SLIM+SWAN run (green); Eulerian currents from a coupled SLIM+SWAN run (orange); and Eulerian currents from and uncoupled SLIM run and Stokes drift from a coupled SLIM+SWAN run on the inner (\textbf{A}) and outer shelves (\textbf{B}). The bottom panels show the comparison of the trajectories of particles advected by Eulerian currents from an uncoupled SLIM run and Stokes drift from coupled and uncoupled model runs on the inner (\textbf{C}) and outer (\textbf{D}) shelves.}}
    \label{fig:traj}
\end{figure}
